Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding $z\sim2$ Quasars

### 2018-01-28 QPQ9/Submit/qpq9_resubmit_2.tex
Resubmitted the second time.

%\documentclass[12pt,preprint]{aastex}
\documentclass[iop]{emulateapj}
\usepackage{natbib,amsmath,graphicx,longtable,amssymb,latexsym,epsf}
\begin{document}

@@

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$. 
We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in
absorption. The sample selects foreground quasars with precise redshift measurements, using 
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the 
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the 
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4}, 
and \ion{Mg}{2}. We find that the mean absorptions exhibit large velocity widths 
$\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational 
motion and Hubble flow, and galactic-scale outflows are not be required to explain the large
widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift. 
The mean absorption centroids exhibit small redshift relative to the 
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid 
velocities of the individual absorption systems. We show that the observed offsets may be produced 
if (i) the ionizing radiation from the foreground quasars is anisotropic or intermittent; (ii) the 
gas is not flowing into the galaxy.  
\end{abstract}

@@

With absorption-line spectroscopy of background sightlines, other researchers also have had 
success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net 
large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on 
1\textendash2\,Mpc scales. \cite{Ho+17} found gas spiraling inward near the disk plane of 
star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding 
$z\sim1$ quasars. They found large peculiar motions in the gas exceeding the expected virial 
velocity, with quasar-driven outflows being one possible explanation. However, we consider that 
their velocity spreads can be better quantified. Other 
existing studies that found large velocity spreads are limited to single sightlines with most of 
the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11,RudieNewmanMurphy17}, 
or with gas tracing 
a higher ionization state than the QPQ absorption systems \citep[e.g., ][]{Churchill+12}, or where 
the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier13}, where a
single sightline is reported, the $\Delta v_{90}$ of the \ion{Mg}{2} absorption is less than the 
average of the QPQ8 \ion{C}{2} absorption. In \cite{Muzahid+15}, an absorber is found with 
$\Delta v_{90}$ smaller than $555\,{\rm km\,s^{-1}}$ in \ion{O}{6} and \ion{N}{5}, and still 
smaller for other ions. The \cite{Zahedy+16} sample likewise has average $\Delta v_{90}$ smaller 
than that of QPQ8.

@@

We create composite spectra that average over the intrinsic scatter in quasar environments, 
continuum placement errors, and redshift errors. The individual spectra of background quasars are 
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum 
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to 
a common spectral resolution. The individual spectra are then combined with a mean or a median 
statistic. Bad pixels in the individual spectra have been masked before generating the 
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the 
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather 
than scatter in the flux of individual observations. The mean statistic of the individual spectra 
yields a good estimate of the average absorption and preserves equivalent width. The median 
statistic is less sensitive to outliers, however the median opacity at any velocity channel is 
rather small, since the discrete absorbers are spread throughout the entire velocity window. The 
analysis on the median velocity field is thus subject to larger uncertainty. In the following we 
present stacked spectra using both the mean and the median statistic.

In Figure~\ref{fig:stacks_and_fits}, we present mean and median stacks of \ion{C}{2}\,1334, 
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 absorption of the QPQ9 sample. We focus on the 
analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
and it is more challenging to analyze their kinematics.
%To assess the average absorption of these transitions,
%we have combined the data with a novel technique.
%We have fitted the combined dataset using a cubic b-spline
%with knots at every 100\,kms.  We weighted each data
%point by the velocity width of the pixel to insure that 
%each sightline makes an equal contribution to the stack.
%These b-spline profiles are presented in the figure
%and a trivial integration gives the reported equivalent
%widths.
%[consider down-weighting systems with $<3\sigma$ EW]
%[Comnent on EW from 'standard' technique]
Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
skewed toward positive velocities. We have 40 pairs in the QPQ9 sample for \ion{C}{2} analysis
and an even larger number of pairs for \ion{C}{4} and \ion{Mg}{2} analyses, and the total number
of individual components can only be larger than the number of absorption systems. Hence, although
QPQ8 showed the distribution of absorbing components in velocity is non-Gaussian for each
individual quasar-host associated system, the central limit theorem applies and the distribution
of all absorbing components should tend toward Gaussian distribution. A visual inspection of the 
stack confirms that a broader absorption component is not apparent. Therefore, to model the 
absorption, we may introduce a Gaussian profile while allowing a constant pseudo-continuum level 
to vary. We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit 
to the data, we measure the centroid of the \ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$ and
the $1\sigma$ dispersion to be $293\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that
contradicts the standard expectation, while the dispersion suggests extreme kinematics. The median 
stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid with 
smaller offset and comparable dispersion.

@@

To model the mean and median absorption of \ion{C}{4}\,1548 and \ion{Mg}{2}\,1796, we introduce a  
second Gaussian with separation equal to the doublet separation ($498\,{\rm km\,s^{-1}}$ and 
$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. We
allow the doublet ratio to vary from 2:1 to 1:1. The modeling results show that the velocity fields
of \ion{C}{4} and \ion{Mg}{2} are consistent with \ion{C}{2}, i.e.\ large dispersion and centroid
is skewed toward positive velocities.

@@

@@

In Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian 
absorption model of the Monte Carlo simulations. In the figure, the Gaussian absorption model is 
broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$. This is
about 2 times the modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack 
for the full sample, and about 2 times the modeling error away from the intrinsic dispersion in the
stack of the sub-sample with [\ion{O}{3}] redshifts as well. We also test for the
sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering 
analysis is performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$ 
sightline may in fact intercept more than one optically thick absorber. We double the number of 
absorbers for each mock sightline, and find the measured dispersion only increases by several 
${\rm km\,s^{-1}}$. Thus, the hypothesis that the observed velocity width is only produced by a 
combination of gravitational motions and Hubble flows cannot be ruled out. Extra dynamical 
processes are not necessary to explain the large velocity fields.

@@

\begin{figure*}[!th]
\begin{minipage}[!bp]{0.28\textwidth}
%\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
\includegraphics[width=\textwidth]{f08.pdf}
\caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion 
absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation. 
}
\label{fig:monopolar}
\end{minipage}%
\hspace{0.3in}
\begin{minipage}[!bp]{0.67\textwidth}
%\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
\includegraphics[width=\textwidth]{f09.pdf}
\caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the 
asymmetric absorption. The setup on the left shows that the foreground quasar has not been shining 
long enough for its ionizing radiation to reach the gas behind it, when the light from the 
background quasar reaches. The setup on the right shows the scenario after an amount of time 
comparable to the light travelling time across CGM scale. Gas in front of the foreground quasar 
has been ionized, by the time the light from the background quasar reaches. 
}
\label{fig:lighttravel}
\end{minipage}
\end{figure*}

@@

In the following, we explore two possible explanations for the putative non-dynamical process that
provides the asymmetry.

One possibility is an asymmetric radiation field that preferentially ionizes the gas moving toward 
the observer, where the quasar is known to shine. Alternatively, the asymmetric radiation field 
may preferentially ionizes the gas at smaller Hubble velocity than the quasar. In 
Figure~\ref{fig:monopolar}, we show a cartoon of a quasar that is blocked in the direction 
pointing away from the observer. The gas observed in absorption preferentially lies behind the 
quasar. The asymmetric absorption arises from a transverse proxmity effect. 
\cite{Roos+15} and \cite{GaborBournaud14} performed simulations of a high-redshift disk galaxy 
including thermal AGN feedback and calculated radiative transfer in post-processing. They found 
the ionization radiation is typically asymmetric, due to either a dense clump that lies on one 
edge of the black hole or the black hole's location being slightly above the disk.
\cite{FaucherGiguere+16} represents the only simulation so far that is able to reproduce the
substantial amount of cool gas in quasar-mass haloes. We eagerly await their group to compare the
fraction of gas in inflows and outflows.

As a test of reasonableness, we calculate that, for a quasar opening angle of $120^\circ$ and
keeping $\sigma_{\rm rms}$ at the expected value for the typical QPQ9 halo, our Monte Carlo
simulations may reproduce the observed centroid and intrinsic dispersion of the \ion{C}{2} mean
absorption to within the modeling error.

Another possible explanation arises from the finite lifetime of quasar episodes. 
Figure~\ref{fig:lighttravel} presents a cartoon for a light travel time argument. Light from the 
background quasar will travel smaller distance to reach the gas behind the foreground quasar 
than the gas in front of it. The light from the background quasar may arrive at the gas behind 
the foreground quasar before the ionizing radiation from the foreground quasar arrives. In 
QPQ7 and QPQ8, we reported that the enhancement in metal ion absorption relative to IGM average 
extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of 
$\sim10^6$\,yr, which lies within existing constraints of quasar lifetime from observations 
\citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.

%As a test of reasonableness, we calculate that, at $R_\perp\approx50\textendash150$\,kpc, radial
%speeds relative to the foreground quasar of $500\textendash700\,{\rm km\,s^{-1}}$ and quasar
%opening angles of $120^\circ\textendash140^\circ$ may reproduce the observed centroid and
%intrinsic dispersion of the \ion{C}{2} mean absorption.
The first explanation above to asymmetric
absorption requires that the quasars emit their ionizing radiation anisotropically, while the 
second explanation requires the quasars emit their ionizing radiation intermittently. Both 
explanations will require the line-of-sight motions of the gas to be in either outflow or Hubble 
flow. Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
Under both scenarios, lows ions should be redshifted while high ions should be blueshifted.
Using Cloud photoionization models, we find that, for the typical quasar luminosity of our sample,
a CGM gas that is directly illuminated is highly ionized and shows only marginally detectable
\ion{C}{4} absorption. The redshifted \ion{C}{4} may be regarded as an intermediate, and a
blueshifted absorption signal needs to be searched in a higher ion.

Motivated by the asymmetry found in metal ion absorption in the CGM using precise $z_{\rm fg}$ 
measurements, and the asymmetry found by \cite{KirkmanTytler08} in \ion{H}{1} on larger 
scales, we are assembling a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study 
this asymmetry in \ion{H}{1} (J. F. Hennawi et al. 2017, in preparation). In conclusion, we 
observe large and positively skewed velocity fields in absorption, of metal ions 
in the CGM of $z\sim2$ massive galaxies hosting quasars. We argue that the velocity fields can be 
explained if the detected gas is in gravitational motion, Hubble flow, or outflow, and the quasars 
either shine preferentially toward the observer or shine intermittently.

@@

JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1010004 and 
AST-1412981. The authors gratefully acknowledge the support which enabled these observations at 
the Keck, Gemini, Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar 
Observatories. The authors acknowledge the sharing of private data by Yue Shen. MWL thanks Hai Fu
for a discussion on extended emission-line regions, T.-K. Chan for a discussion on CGM
simulations, and Chi Po Choi for a discussion on statistics.

>>>>

%\documentclass[12pt,preprint]{aastex}
\documentclass[iop]{emulateapj}
\usepackage{natbib,amsmath,graphicx,longtable,amssymb,latexsym,epsf,sidecap}
\begin{document}

@@

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$.
We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in
absorption. The sample selects foreground quasars with precise redshift measurements, using
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4},
and \ion{Mg}{2}. We find that the mean absorptions exhibit large velocity widths
$\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational
motion and Hubble flow, and galactic-scale outflows are not required to explain the large
widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift.
The mean absorption centroids exhibit small redshift relative to the
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid
velocities of the individual absorption systems. We show that the observed offsets may be produced
if (i) the ionizing radiation from the foreground quasars is anisotropic or intermittent; (ii) the
gas is not flowing into the galaxy.
\end{abstract}

@@

With absorption-line spectroscopy of background sightlines, other researchers also have had
success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net
large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on
1\textendash2\,Mpc scales. \cite{Ho+17} found gas spiraling inward near the disk plane of
star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding
$z\sim1$ quasars. They found large peculiar motions in the gas exceeding the expected virial
velocity, with quasar-driven outflows being one possible explanation. However, we consider that
their velocity spreads can be better quantified. Other
existing studies that found large velocity spreads are {\bf single sightlines
\citep[e.g.,][]{Tripp+11,RudieNewmanMurphy17}}, or with gas tracing
a higher ionization state than the QPQ absorption systems \citep[e.g.,][]{Churchill+12}, or where
the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier13}, where a
single sightline is reported, the $\Delta v_{90}$ of the \ion{Mg}{2} absorption is less than the
average of the QPQ8 \ion{C}{2} absorption. In \cite{Muzahid+15}, an absorber is found with
$\Delta v_{90}$ smaller than $555\,{\rm km\,s^{-1}}$ in \ion{O}{6} and \ion{N}{5}, and still
smaller for other ions. The \cite{Zahedy+16} sample likewise has average $\Delta v_{90}$ smaller
than that of QPQ8.

@@

We create composite spectra that average over the intrinsic scatter in quasar environments,
continuum placement errors, and redshift errors. The individual spectra of background quasars are
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to
a common spectral resolution.
The individual spectra are then combined with a mean or a median
statistic.
{\bf Spectra with broad absorption-line systems and mini-broad absorption-line systems are excluded.}
Bad pixels in the individual spectra have been masked before generating the
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather
than scatter in the flux of individual observations. The mean statistic of the individual spectra
yields a good estimate of the average absorption and preserves equivalent width. The median
statistic is less sensitive to {\bf outliers. However, the median opacity at any velocity channel is
rather small, since the discrete absorbers are spread throughout the entire velocity window.
A pixel is not affected unless there are more than 50\% of quasar pairs with absorption at its
velocity.} The analysis on the median velocity field is thus subject to larger uncertainty. In the
following we present stacked spectra using both the mean and the median statistic.

In Figure~\ref{fig:stacks_and_fits}, we present mean and median stacks of \ion{C}{2}\,1334,
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 absorption of the QPQ9 sample. We focus on the
analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions
and it is more challenging to analyze their kinematics.
%To assess the average absorption of these transitions,
%we have combined the data with a novel technique.
%We have fitted the combined dataset using a cubic b-spline
%with knots at every 100\,kms.  We weighted each data
%point by the velocity width of the pixel to insure that
%each sightline makes an equal contribution to the stack.
%These b-spline profiles are presented in the figure
%and a trivial integration gives the reported equivalent
%widths.
%[consider down-weighting systems with $<3\sigma$ EW]
%[Comnent on EW from 'standard' technique]
Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely
skewed toward positive velocities.

{\bf Visually, there are two absorption components. One component is the uniform depression in the
continuum level in the stack resulting from absorbers unassociated with the foreground
quasars. The other component comes from absorbers associated with the foreground quasars and
distribute around their systemic velocities. To model the absorption, we introduce
a Gaussian profile while allowing a constant ``pseudo-continuum'' to vary.}
We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit
to the data, we measure the centroid of the \ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$ and
the $1\sigma$ dispersion to be $293\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that
contradicts the standard expectation, while the dispersion suggests extreme kinematics. The median
stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid with
smaller offset and a more uncertain dispersion.

{\bf To test whether the dispersion in the average absorption associated with the foreground quasars is
well-captured by a Gaussian model, we also calculate the dispersion separately using the standard
deviation formula. Specifically, we apply the standard deviation formula to a $\pm1300\,{\rm km\,s^{-1}}$
window surrounding the absorption centroid, while fitting a continuum to the rest of the
$\pm3000\,{\rm km\,s^{-1}}$ window for stacking. The
dispersion measured with the above method is essentially the same as that found by fitting a Gaussian.
One may also speculate on the existence of a broader absorption component hidden in the depressed
continuum. We try replacing the constant absorption component with a broad Gaussian component in our
modeling. We find that this second Gaussian component has essentially the same amplitude as the initial
constant absorption component, and is wider than the entire velocity window for stacking.
This weak and very broad component has no effect on the centroid and width of the narrow,
associated Gaussian component. We therefore consider that one single Gaussian component is a good
description of the average absorption associated with the foreground quasars.
Moreover, narrow associated absorbers of background quasars will not prefer the systemic velocities of
the foreground quasars, and hence will not affect the average absorption measured for the foreground
quasars. Their contribution to the average absorption should result in a tilt in the
pseudo-continuum, which is insignificant.}

@@

To model the mean and median absorption of \ion{C}{4}\,1548 and \ion{Mg}{2}\,1796, we introduce a
second Gaussian with separation equal to the doublet separation ($498\,{\rm km\,s^{-1}}$ and
$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. We
allow the doublet ratio to vary from 2:1 to 1:1.
{\bf The centroid is degenerate with the doublet ratio in our modeling. This degeneracy is more
pronounced for \ion{C}{4}, although we find that a double ratio closer to 2:1 better captures the
absorption at the central few pixels. We state that the modeling of the doublets is presented for
consistency check, but the analysis focuses on \ion{C}{2}.}
The modeling results show that the velocity fields
of \ion{C}{4} and \ion{Mg}{2} are consistent with \ion{C}{2}, i.e.\ large dispersion and centroid
is skewed toward positive velocities.

@@

{\bf One may ask whether absorption from \ion{C}{2*}\,1335 may bias the measurement of the
\ion{C}{2}\,1334 velocity centroid. In the stacks at \ion{C}{2*}\,1334, absorption from \ion{C}{2*}\,1335
would manifest as a component redshifted by $+264\,{\rm km\,s^{-1}}$.
In the higher resolution data from QPQ8, we identify nine \ion{C}{2}-bearing subsystems where absorption
from \ion{C}{2*}\,1335 is not blended with \ion{C}{2}\,1334. Among these nine subsystems, only one,
labeled J1420+1603F in QPQ8, has a \ion{C}{2*}\,1335 equivalent width comparable to \ion{C}{2}\,1334.
Hence, contamination from \ion{C}{2*}\,1335 is insignificant and could not be responsible for the
observed redshift in the centroid.}

@@

In Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian
absorption model of the Monte Carlo simulations. In the figure, the Gaussian absorption model is
broadened by the mean redshift error by adding it in quadrature to the dispersion in the model, and
is arbitrarily shifted to match the centroid in the stack of observations.
The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$. This is
about 2 times the modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack
for the full sample, and about 2 times the modeling error away from the intrinsic dispersion in the
stack of the sub-sample with [\ion{O}{3}] redshifts as well. We also test for the
sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering
analysis is performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$
sightline may in fact intercept more than one optically thick absorber. We double the number of
absorbers for each mock sightline, and find the measured dispersion only increases by several
${\rm km\,s^{-1}}$. Thus, the hypothesis that the observed velocity width is only produced by a
combination of gravitational motions and Hubble flows cannot be ruled out. Extra dynamical
processes are not necessary to explain the large velocity fields.

{\bf Although we acknowledge the possibility that our Gaussian model does not capture all the powers
at extreme velocities, we also caution that occasional large kinematic offsets do not make a strong
case against gravitational motions. Firstly, quasars occasionally inhabit extremely overdense environments
such as protoclusters \citep[e.g.,][]{Hennawi+15}. Secondly, the probability of intercepting a random,
unassociated absorber is boosted by large-scale clustering. Hence occasional extreme velocities would not
necessitate outflows. Our preferred kinematic measure is thus the dispersion in the average absorption.}

@@

%\begin{figure*}[!th]
%\begin{minipage}[!bp]{0.28\textwidth}
%%\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
%\includegraphics[width=\textwidth]{f08.pdf}
%\caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion
%absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation.
%}
%\label{fig:monopolar}
%\end{minipage}%
%\hspace{0.3in}
%\begin{minipage}[!bp]{0.67\textwidth}
%%\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
%%\includegraphics[width=\textwidth]{f09.pdf}
%\caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the
%asymmetric absorption. The setup on the left shows that the foreground quasar has not been shining
%long enough for its ionizing radiation to reach the gas behind it, when the light from the
%background quasar reaches. The setup on the right shows the scenario after an amount of time
%comparable to the light travelling time across CGM scale. Gas in front of the foreground quasar
%has been ionized, by the time the light from the background quasar reaches.
%}
%\label{fig:lighttravel}
%\end{minipage}
%\end{figure*}

\sidecaptionvpos{figure}{c}
\begin{SCfigure*}[10][!th]
%\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
\includegraphics[height=0.49\textheight]{f08.pdf}
\caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion
absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation.}
\label{fig:monopolar}
\end{SCfigure*}
\sidecaptionvpos{figure}{c}
\begin{SCfigure*}[10][!bh]
%\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
\includegraphics[height=0.49\textheight]{f09.pdf}
\caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the
asymmetric absorption. The setup on the left shows that the foreground quasar has not been shining
long enough for its ionizing radiation to reach the gas behind it, when the light from the
background quasar reaches. The setup on the right shows the scenario after an amount of time
comparable to the light travelling time across CGM scale. Gas in front of the foreground quasar
has been ionized, by the time the light from the background quasar reaches.}
\label{fig:lighttravel}
\end{SCfigure*}

@@

In the following, we explore two possible explanations for the putative non-dynamical process that
provides the asymmetry.
{\bf The explanations arise from a transverse proximity effect (QPQ4), which is the suppression of
opacity in background sightlines passing close to foreground quasars.}

One possibility is an asymmetric radiation field that preferentially ionizes the gas moving toward
the observer, where the quasar is known to shine. Alternatively, the asymmetric radiation field
may preferentially ionizes the gas at smaller Hubble velocity than the quasar. In
Figure~\ref{fig:monopolar}, we show a cartoon of a quasar that is blocked in the direction
pointing away from the observer. The gas observed in absorption preferentially lies behind the
quasar.
\cite{Roos+15} and \cite{GaborBournaud14} performed simulations of a high-redshift disk galaxy
including thermal AGN feedback and calculated radiative transfer in post-processing. They found
the ionization radiation is typically asymmetric, due to either a dense clump that lies on one
edge of the black hole or the black hole's location being slightly above the disk.
\cite{FaucherGiguere+16} represents the only simulation so far that is able to reproduce the
substantial amount of cool gas in quasar-mass haloes. We eagerly await their group to compare the
fraction of gas in inflows and outflows.

{\bf As a test of reasonableness, we try implementing an arbitrary quasar opening angle in our
Monte Carlo simulations to reproduce an absorption centroid that is redshifted from the systemic.
In this test, we remove all absorbers at circumgalactic distances that fall within the quasar
opening angle. We find that, for an opening angle of $120^\circ$ and keeping $\sigma_{\rm rms}$ at
the expected value for the typical QPQ9 halo, the observed centroid and intrinsic dispersion of the
\ion{C}{2} mean absorption may be reproduced within modeling errors.}

Another possible explanation arises from the finite lifetime of quasar episodes.
Figure~\ref{fig:lighttravel} presents a cartoon for a {\bf light travel time argument. The light from}
the background quasar may arrive at the gas behind
the foreground quasar before the ionizing radiation from the foreground quasar arrives. In
QPQ7 and QPQ8, we reported that the enhancement in metal ion absorption relative to IGM average
extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of
$\sim10^6$\,yr.
In turn, this implies a minimum quasar lifetime of $10^6$\,yr, which lies within existing
constraints from
observations \citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.

The first explanation above to asymmetric
absorption requires that the quasars emit their ionizing radiation anisotropically, while the
second explanation requires the quasars emit their ionizing radiation intermittently. Both
explanations will require the line-of-sight motions of the gas to be in either outflow or Hubble
flow. Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
Under both scenarios, lows ions should be redshifted while high ions should be blueshifted.
Using Cloud photoionization models, we find that, for the typical quasar luminosity of our sample,
a CGM gas that is directly illuminated is highly ionized and shows only marginally detectable
\ion{C}{4} absorption. The redshifted \ion{C}{4} may be regarded as an intermediate, and a
blueshifted absorption signal needs to be searched in a higher ion.

Motivated by the asymmetry found in metal ion absorption in the CGM using precise $z_{\rm fg}$
measurements, and the asymmetry found by \cite{KirkmanTytler08} in \ion{H}{1} on larger
scales, we are assembling a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study
this asymmetry in \ion{H}{1} (J.\ F.\ Hennawi et al.\ 2017, in preparation). In conclusion, we
observe large and positively skewed velocity fields in absorption, of metal ions
in the CGM of $z\sim2$ massive galaxies hosting quasars.
{\bf We argue that the large velocity fields can be accounted for by gravitational motions and
Hubble flows and do not necessitate outflows. Further, the positive skew can be explained if the
detected gas is not in inflow on average, and the quasars either shine preferentially toward the
observer or shine intermittently.}

@@

{\bf MWL is immensely grateful to the referee's constructive comments, which help strengthen the
paper.}
JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1010004 and
AST-1412981. The authors gratefully acknowledge the support which enabled these observations at
the Keck, Gemini, Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar
Observatories. The authors acknowledge the sharing of private data by Yue Shen. MWL thanks Hai Fu
for a discussion on extended emission-line regions, T.-K. Chan for a discussion on CGM
simulations, and Chi Po Choi {\bf and Yat Tin Chow for discussions} on statistics.
